Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-06 paper.tex
Modified section 3, paragraph 4

Secondly, the daily and hourly distribution of queries appear to correspond with known commuting patterns. 
\cref{fig:average} depicts an break down of the queries that occur on an hourly basis for each day of the week.
Several trends can be observed in this chart. 
Morning and evening peak periods in particular, are clearly distinguishable.
In this regard, the peak hours on weekdays are distinctively different from those of the weekends. 
Similarly, the frequency of queries during the morning peak period on Fridays appear to be substantially lower than those that occur between Monday and Thursday.
The discrepancy maybe explained by a decrease in the number students who travel home from college over the weekends. \todo{Can we give a link to more reading material about this behaviour? This might be weird for US people? --> not sure if this is really case. We need to explain this in a clear way}.
The absence of a clear peak on Saturdays can be attributed to lack of journey to work queries while the evening peak on Sundays may emerge from students returning to college accommodations.

>>>>

Secondly, the daily and hourly distribution of queries appear to correspond with known commuting patterns. 
\cref{fig:average} depicts an break down of the queries that occur on an hourly basis for each day of the week.
Several trends can be observed in this chart. 
Morning and evening peak periods in particular, are clearly distinguishable.
Peak hours on weekdays are also distinctively different from those of weekends.
Similarly, the frequency of queries during the morning peak period on Fridays appear to be substantially lower than those that occur between Monday and Thursday.
The discrepancy maybe explained by a decrease in the number students who travel home from college over the weekends. \todo{Can we give a link to more reading material about this behaviour? This might be weird for US people? --> not sure if this is really case. We need to explain this in a clear way}.
The absence of a clear peak on Saturdays can be attributed to lack of journey to work queries while the evening peak on Sundays may emerge from students returning to college accommodations.

Finally, the distribution of queries on public holidays is observed to deviate from that of an average day. 
Figure 3 provides a breakdown of queries per hour on Christmas eve, 24th December 2015, in comparison to an average Thursday of the same year. 
As illustrated, the evening peak on Christmas eve occurs earlier than that of an average Thursday. 
For these reasons, we believe that route planning query data maybe a viable source of information for flow analysis.
